---
title: "prediction 2"
author: "Basma Tharwat"
date: "March 8, 2019"
output: html_document
code_folding: "hide"
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```
##Read , Explore & Clean the training data
```{r}
training = read.csv("pml-training.csv")
training = training[, -c(1:7)]

# Remove bad columns

bad.col = !apply(training, 2, function(x) sum(is.na(x)) > 0.95*nrow(training) || 
                     sum(x == "") > 0.95*nrow(training))
bad.col[is.na(bad.col) == T] = F
training = training[, bad.col]

# Remove near zero values

suppressMessages(require(caret))

training.zeroVar = nearZeroVar(training, saveMetrics = T)

# Remove incomplete lines

training = training[complete.cases(training), ]

# Assessing the Data

str(training)
```
```{r}
# Assessing correlated col

suppressMessages(require(corrr))

rdf = correlate(subset(training, select = -c(classe)))
rplot(rdf, print_cor = T, legend = T, colours = heat.colors(20, alpha = .5))

```

```{r}
# Using Random Forest

set.seed(2964)


# In this pretest I made a model valuation adjustment using only 5% of the training database. 
# After this step we will use only the most significant with the full dataset training.

inTrain = createDataPartition(training$classe, p = 0.05, list = F)
crossv = training[-inTrain, ]
training2 = training[inTrain, ]

dim(crossv); dim(training2)
```
```{r}
mod = suppressMessages(
    train(classe ~ ., method = "rf", data = training2, 
          trControl = trainControl(method = "cv"), number = 25)
)

mod$finalModel
```


```{r}
pred.test = predict(mod, crossv); confusionMatrix(pred.test, crossv$classe)



```

```{r}

# Create fine tunning

mod.varImp = varImp(mod)
plot(mod.varImp, main = "Importance of all Variables for 'rf' model")
```

```



```{r}


suppressMessages(require(tree))

tr = tree(classe ~ . , data = training)
plot(tr); text(tr, cex = .75)


```

```{r}

testing = read.csv("pml-testing.csv")
testing = testing[, -c(1:7)]
bad.col = !apply(testing, 2, function(x) sum(is.na(x)) > 0.95*nrow(testing) || 
                     sum(x == "") > 0.95*nrow(testing))
bad.col[is.na(bad.col) == T] = F
testing = testing[, bad.col]
testing = testing[complete.cases(testing), ]

pml_write_files = function(x){
    n = length(x)
    for(i in 1:n){
        filename = paste0("problem_id_",i,".txt")
        write.table(x[i],file=filename,quote=FALSE,row.names=FALSE,col.names=FALSE)
    }
}
x = testing


```

```{r pressure, echo=FALSE}

```




